BOLD Parameter Estimation Using Particle Filters

### 2010-09-02 doc/thesis/results.tex
just need to fix figure captions for multivoxel cases. And fix bib

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge}
\caption[\ac{BOLD} estimate converging for a very long \ac{fMRI} run.]{\ac{BOLD} estimate 
converging for a 2400 second \ac{fMRI} run. Darker bars indicate
bins with more regions. }
\label{fig:long_converge}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge_500}
\caption{\ac{BOLD} estimate converging for a very long \ac{fMRI} run, first 500 seconds. Darker bars
indicate bins with more particles.}
\label{fig:long_converge_500}
\end{figure}

@@

%LOW NOISE SECTION, with a signal
\subsection{Simulation with Low Noise}
\label{sec:SimLowNoise}
%tests had noise of $ \{\sigma_y = .01, \sigma_x = .005\} $, where $\sigma_y$ is the
%measurement noise, and $\sigma_x$ is the wiener step size. Both signals used the
%parameters .
%The particle filter used the parameters defined in \autoref{tab:Prior} (\autoref{sec:PriorDistrib}),
%thus the particle filter was not centered over the correct values.
\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/realization_lownoise}
\caption{Test Signals with low noise compared to the clean signal.}
\label{fig:LowNoiseRealization}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_lownoise}
\caption{A comparison of the preprocessed signals for the low noise case. The
noisy input to the actual particle filter algorithm.}
\label{fig:PreprocessedLowNoise}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_lownoise}
\caption{A comparison of the fitted signals for the low noise case.}
\label{fig:FitComparisonLowNoise}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \ac{RMSR} & \ac{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 & 5.1019 &  0.003211  & 0.00224\\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 & 5.1187 &  0.003055  & 0.00223\\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 & 5.1672 &  0.003289  & 0.00205\\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 & 5.0439 &  0.002847  & 0.00147\\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 & 5.0240 &  0.003006  & 0.00213\\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 & 5.0553 &  0.002833  & 0.00184\\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 & 4.9968 &  0.003028  & 0.00255\\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 & 5.1265 &  0.003044  & 0.00238\\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 & 4.9909 &  0.003345  & 0.0027 \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 & 5.0330 &  0.003175  & 0.00244\\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 & 5.0735 &  0.002889  & 0.00188\\
\hline                                                                               
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 & 5.0665 & 0.003066     & 0.00217\\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise. First row is the true value, and last is the average.}
\label{tab:LowNoiseResults}
\end{table}

\begin{figure}
\subfigure[Converging histogram for $\tau_0$, $\alpha$, $E_0$, and $V_0$ of the first run, low noise simulation.]
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=16cm]{images/converge_lownoise1}}\\

\subfigure[Converging histogram for $\tau_s$, $\tau_f$, $\epsilon$, and $v$ of the first run, low noise simulation.]
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=16cm]{images/converge_lownoise2}}\\
\end{figure}

\begin{figure}
\subfigure[Converging histogram for $q$, $s$, $f$, and $BOLD$ of the first run, low noise simulation.]
{\label{fig:LowNoiseHistc} \includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=16cm]{images/converge_lownoise3}}
\caption{Convergence of the first run from \autoref{tab:LowNoiseResults}. The bars represent
a histogram, where darker bars indicate more particles in that bin.}
\label{fig:LowNoiseHist}
\end{figure}

@@

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_highnoise}
\caption{A comparison of the preprocessed signals for the high noise case.}
\label{fig:PreprocessedHighNoise}
\end{figure}

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_highnoise}
\caption{A comparison of the fitted signals for the high noise case.}
\label{fig:FitComparisonHighNoise}
\end{figure}

@@

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \ac{RMSR} & \ac{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.1900 & 0.2349 & 0.4223 & 0.128  & 1.0147 & 2.4779 & 1.1168 & 4.6826 &0.01406 & 0.00859\\
0.9721 & 0.2190 & 0.3051 & 0.061  & 0.5780 & 1.9960 & 3.4613 & 3.5461 &0.01373 & 0.00735\\
1.5795 & 0.1415 & 0.3380 & 0.1089 & 0.5843 & 2.1247 & 1.7834 & 4.2885 &0.01275 & 0.00951\\
1.1094 & 0.2374 & 0.5349 & 0.0351 & 1.2186 & 3.0736 & 2.3504 & 5.4016 &0.01673 & 0.00479 \\
1.1071 & 0.2753 & 0.3365 & 0.0316 & 1.5057 & 2.6518 & 4.1910 & 5.2646 &0.01370 & 0.00475\\
0.5803 & 0.4793 & 0.4135 & 0.1189 & 0.9756 & 3.6902 & 1.0008 & 5.2461 &0.01150 & 0.00672\\
\rowcolor[rgb]{.9,.5,.5}
1.2952 & 0.2596 & 0.2756 & 0.2595 & 1.7026 & 2.8458 & 0.6617 & 5.8436 &0.01555 & 0.01039\\
\rowcolor[rgb]{.5,.5,.9}
1.5185 & 0.2199 & 0.2835 & 0.0742 & 0.8882 & 3.0771 & 1.7393 & 5.4838 &0.01205 & 0.00655\\
0.6874 & 0.3283 & 0.3979 & 0.1561 & 1.0778 & 3.1158 & 0.6643 & 4.8810 &0.01510 & 0.0057 \\
1.0170 & 0.285  & 0.3474 & 0.0567 & 1.5877 & 2.6516 & 2.2852 & 5.2563 &0.01249 & 0.00582\\
0.9925 & 0.298  & 0.3221 & 0.2094 & 0.4276 & 2.2108 & 1.0167 & 3.6308 &0.01217 & 0.00916\\
\hline
1.0954 & 0.2708 & 0.3615 & 0.1126 & 1.0510 & 2.7196 & 1.8428 & 4.8659 &0.01362 & 0.00721\\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with high noise. First row contains the true parameters,
last row contains the mean.
The red row is Run 1 and the blue row is Run 2 from  \autoref{fig:NoiseComparisonJustTwo}
and \autoref{fig:FitComparisonHighNoiseJust2}, respectively.}
\label{tab:HighNoiseResults}
\end{table}

@@

\begin{figure}[H]
\subfigure[$\tau_0$, $\alpha$, $E_0$, $V_0$, Run 1]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=14cm]{images/highnoise_run5_1}}\\
\end{figure}

\begin{figure}[H]
\subfigure[$\tau_s$, $\tau_f$, $\epsilon$, $v$, Run 1]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=14cm]{images/highnoise_run5_2}}\\
\end{figure}

\begin{figure}[H]
\subfigure[$q$, $s$, $f$, $BOLD$, Run 1 ]
{\label{fig:ConvergenceRuns1c} \includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=14cm]{images/highnoise_run5_3}}
\caption{Converging histogram for parameters during run 1, as in \autoref{fig:NoiseComparisonJustTwo}.}
\label{fig:ConvergenceRuns1}
\end{figure}

\begin{figure}[H]
\subfigure[$\tau_0$, $\alpha$, $E_0$, $V_0$, Run 2]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=14cm]{images/highnoise_run6_1}}\\
\end{figure}

\begin{figure}[H]
\subfigure[$\tau_s$, $\tau_f$, $\epsilon$, $v$, Run 2]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=14cm]{images/highnoise_run6_2}}\\
\end{figure}

\begin{figure}[H]
\subfigure[$q$, $s$, $f$, $BOLD$, Run 2 ]
{\label{fig:ConvergenceRuns2c} \includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=14cm]{images/highnoise_run6_3}}
\caption{Converging histogram for parameters during run 2, as in \autoref{fig:NoiseComparisonJustTwo}.}
\label{fig:ConvergenceRuns2}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 6cm 3.5cm,width=15cm]{images/preprocessed_noiseonly}
\caption{Comparison of the preprocessed signals for the low noise signal-free case (
$\sigma_y = 0.01, \sigma_x = 0.005$).}
\label{fig:PreprocessedNoiseOnly}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & \ac{RMSR} \\
\hline
1.0324 & 0.33211 & 0.34058 & 0.03012 & 1.40665 & 2.52079 & 0.5311 &   0.00167  \\
 0.98189 & 0.33047 & 0.3386 & 0.03014 & 1.45707 & 2.47232 & 0.45049 & 0.00159   \\
 1.0429 & 0.33224 & 0.34124 & 0.02946 & 1.4618 & 2.49245 & 0.43012 &  0.00165   \\
 1.02054 & 0.3321 & 0.33484 & 0.02586 & 1.45848 & 2.48741 & 0.4193 &  0.00151   \\
 1.0565 & 0.33405 & 0.33758 & 0.02791 & 1.43784 & 2.52545 & 0.47517 & 0.00152   \\
 1.01867 & 0.33528 & 0.33918 & 0.02782 & 1.48345 & 2.49605 & 0.44209 &0.00156   \\
 1.051 & 0.33038 & 0.33837 & 0.02985 & 1.47651 & 2.48621 & 0.42719 &  0.00159   \\
 1.00281 & 0.32929 & 0.33988 & 0.0298 & 1.43519 & 2.49256 & 0.48899 & 0.00164   \\
 1.00893 & 0.33273 & 0.33982 & 0.0289 & 1.42903 & 2.49754 & 0.45688 & 0.00168   \\
 1.01289 & 0.33275 & 0.3376 & 0.02997 & 1.41188 & 2.49881 & 0.50628 & 0.00183   \\
 1.10247 & 0.33371 & 0.3419 & 0.02939 & 1.43774 & 2.53384 & 0.44079 & 0.00195   \\
\hline
1.03009 & 0.33228 & 0.33905 & 0.02902 & 1.44506 & 2.50031 & 0.46076 & 0.00165 \\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise and no signal present.}
\label{tab:NoiseOnlyResults}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/fits_noiseonly}
\caption{Fits to the non-active, low noise signal. Note that the line is thick because all
the estimates overlap. All 11 fitted lines.}
\label{fig:fits_noiseonly}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justnoise_fit_0}
\caption{Fit from a single particle filter run, with the noise input. }
\label{fig:justnoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

\begin{figure}[H]
\centering
\subfigure[$\tau_0$, $\alpha$, $E_0$, $V_0$]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, height=9cm]{images/justnoise_hist_1}}\\
\end{figure}

\begin{figure}[H]
\centering
\subfigure[$\tau_s$, $\tau_f$, $\epsilon$, $v$]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, height=9cm]{images/justnoise_hist_2}}\\
\end{figure}

\begin{figure}[H]
\centering
\subfigure[$q$, $s$, $f$, $BOLD$ ]
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, height=9cm]{images/justnoise_hist_3}}
\caption{Converging histogram for parameters when the signal consists purely of low level noise.
Same run as \autoref{fig:justnoise_fit_0}}
\label{fig:JustNoiseConvergence}
\end{figure}

The data shows that the parameters did not converge
(\autoref{fig:JustNoiseConvergence}).
The peaks never even reached 1\% difference
(\autoref{fig:PreprocessedNoiseOnly}) so  the signal  stayed
well within the range of $0.005$, the standard deviation of the weighting function.
Note that the \acs{RMSR}
were actually lower than the \acs{RMSR} in the low noise simulation 
from \autoref{sec:SimLowNoise}
and the parameter estimates were more consistent across 11 runs.
The low \ac{RMSR} was caused by the overall
signal being significantly smaller than any previous simulation.
This run would benefit greatly from an adaptive weight function, since
such a much tighter weighting function would have forced the particle
filter to fail.

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3cm,width=15cm]{images/fits_noiseonly_high}
\caption{\ac{BOLD} estimates for the non-active, high noise signal. Note the line thickness is caused
by all the estimates overlapping.}
\label{fig:fits_noiseonly_high}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justbignoise_fit_0}
\caption{Fit from a single particle filter run, with the noise input. }
\label{fig:justbignoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

>>>>

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge}
\caption[\ac{BOLD} estimate converging for a very long \ac{fMRI} run.]{\ac{BOLD} estimate 
converging for a 2400 second \ac{fMRI} run. Darker bars indicate
bins with more particles with BOLD estimate in that range. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:long_converge}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=1cm 0cm 0cm 0cm, width=17cm]{images/long_converge_500}
\caption[First 500 seconds of the \ac{BOLD} estimate converging for a very 
long \ac{fMRI} run.]{First 500 seconds of \ac{BOLD} estimate 
converging for a 2400 second \ac{fMRI} run. Darker bars indicate
bins with more particles with BOLD estimate in that range. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:long_converge_500}
\end{figure}

@@

%LOW NOISE SECTION, with a signal
\subsection{Simulation with Low Noise}
\label{sec:SimLowNoise}
%tests had noise of $ \{\sigma_y = .01, \sigma_x = .005\} $, where $\sigma_y$ is the
%measurement noise, and $\sigma_x$ is the wiener step size. Both signals used the
%parameters .
%The particle filter used the parameters defined in \autoref{tab:Prior} (\autoref{sec:PriorDistrib}),
%thus the particle filter was not centered over the correct values.
\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/realization_lownoise}
\caption[Simulated Signal with Low Noise/Drift]
{Simulated signals with different noise realizations compared to true
signal. ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:LowNoiseRealization}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_lownoise}
\caption[Preprocessed Signal with Low Noise/Drift]
{Results of preprocessing compared to the true signal. 
 Knots of spline placed every 20 measurements.
 ($\sigma_x = 0.0005$, $\sigma_y = 0.001$)}
\label{fig:PreprocessedLowNoise}
\end{figure}

\begin{figure}
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_lownoise}
\caption[Results with Low Noise/Drift]
{Results of the particles filter with preprocessed signals from \autoref{fig:PreprocessedLowNoise}
as input.}
\label{fig:FitComparisonLowNoise}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \acs{RMSR} & \acs{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.2221 & 0.3449 & 0.3346 & 0.0714 & 1.6045 & 2.2753 & 1.5945 & 5.1019 &  0.003211  & 0.00224\\
1.3749 & 0.3318 & 0.3630 & 0.0733 & 1.6408 & 2.1030 & 1.5763 & 5.1187 &  0.003055  & 0.00223\\
1.1660 & 0.3221 & 0.3406 & 0.0822 & 1.6477 & 2.3535 & 1.2452 & 5.1672 &  0.003289  & 0.00205\\
1.2318 & 0.3271 & 0.3403 & 0.0796 & 1.6270 & 2.1852 & 1.3033 & 5.0439 &  0.002847  & 0.00147\\
1.1832 & 0.3179 & 0.3472 & 0.0821 & 1.5496 & 2.2912 & 1.2782 & 5.0240 &  0.003006  & 0.00213\\
1.1424 & 0.334  & 0.3473 & 0.0737 & 1.6221 & 2.2908 & 1.4025 & 5.0553 &  0.002833  & 0.00184\\
1.3004 & 0.3596 & 0.3564 & 0.0768 & 1.5641 & 2.1323 & 1.6034 & 4.9968 &  0.003028  & 0.00255\\
1.2401 & 0.3460 & 0.3398 & 0.0891 & 1.6499 & 2.2366 & 1.2900 & 5.1265 &  0.003044  & 0.00238\\
1.1709 & 0.3274 & 0.3464 & 0.0826 & 1.5373 & 2.2826 & 1.3783 & 4.9909 &  0.003345  & 0.0027 \\
1.1897 & 0.3434 & 0.3355 & 0.0798 & 1.5358 & 2.3075 & 1.4277 & 5.0330 &  0.003175  & 0.00244\\
1.184 &  0.3405 & 0.3502 & 0.0892 & 1.6103 & 2.2793 & 1.1645 & 5.0735 &  0.002889  & 0.00188\\
\hline                                                                               
1.2187 & 0.3359 & 0.3456 & 0.0800 & 1.599 & 2.2488 & 1.3876 & 5.0665 & 0.003066     & 0.00217\\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise. First row is the true value, 
last is the average. $\sum \tau$ is the sum of the estimated time constants.}
\label{tab:LowNoiseResults}
\end{table}

\begin{figure}
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/converge_lownoise1}}
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/converge_lownoise2}}
\end{figure}

\begin{figure}
\subfigure
{\label{fig:LowNoiseHistc} \includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/converge_lownoise3}}
\caption[Convergence of the parameters from the first run of \autoref{tab:LowNoiseResults}.]
{Convergence of the parameters from the first run of \autoref{tab:LowNoiseResults}. 
Order of estimates: $\tau_0, \alpha, E_0, V_0, \tau_s, \tau_f, \epsilon, v,
q, s, f, BOLD$.  The bars represent
a histogram, where darker bars indicate more particles with parameters in that bin. The red 
line is the parameter used to generate the true signal, blue line is the final mean of the
particles.}
\label{fig:LowNoiseHist}
\end{figure}

@@

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/preprocessed_highnoise}
\caption[Preprocessed Signal with High Noise/Drift]
{Results of preprocessing compared to the true signal.  
 Knots of spline placed every 20 measurements. ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{fig:PreprocessedHighNoise}
\end{figure}

\begin{figure}
\includegraphics[clip=true,trim=6cm 2cm 5cm 3.5cm,width=15cm]{images/comparison_highnoise}
\caption[Results with High Noise/Drift]
{Results of the particles filter with preprocessed signals from \autoref{fig:PreprocessedHighNoise}
as input.}
\label{fig:FitComparisonHighNoise}
\end{figure}

@@

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & $ \sum \tau $ & \acs{RMSR} & \acs{RMSE} \\
\hline
\rowcolor[gray]{.8}
1.45 & 0.3 & 0.47 & 0.044 & 1.94 & 1.99 & 1.8  & 5.38 &  & \\
\hline
\hline
1.1900 & 0.2349 & 0.4223 & 0.128  & 1.0147 & 2.4779 & 1.1168 & 4.6826 &0.01406 & 0.00859\\
0.9721 & 0.2190 & 0.3051 & 0.061  & 0.5780 & 1.9960 & 3.4613 & 3.5461 &0.01373 & 0.00735\\
1.5795 & 0.1415 & 0.3380 & 0.1089 & 0.5843 & 2.1247 & 1.7834 & 4.2885 &0.01275 & 0.00951\\
1.1094 & 0.2374 & 0.5349 & 0.0351 & 1.2186 & 3.0736 & 2.3504 & 5.4016 &0.01673 & 0.00479 \\
1.1071 & 0.2753 & 0.3365 & 0.0316 & 1.5057 & 2.6518 & 4.1910 & 5.2646 &0.01370 & 0.00475\\
0.5803 & 0.4793 & 0.4135 & 0.1189 & 0.9756 & 3.6902 & 1.0008 & 5.2461 &0.01150 & 0.00672\\
\rowcolor[rgb]{.9,.5,.5}
1.2952 & 0.2596 & 0.2756 & 0.2595 & 1.7026 & 2.8458 & 0.6617 & 5.8436 &0.01555 & 0.01039\\
\rowcolor[rgb]{.5,.5,.9}
1.5185 & 0.2199 & 0.2835 & 0.0742 & 0.8882 & 3.0771 & 1.7393 & 5.4838 &0.01205 & 0.00655\\
0.6874 & 0.3283 & 0.3979 & 0.1561 & 1.0778 & 3.1158 & 0.6643 & 4.8810 &0.01510 & 0.0057 \\
1.0170 & 0.285  & 0.3474 & 0.0567 & 1.5877 & 2.6516 & 2.2852 & 5.2563 &0.01249 & 0.00582\\
0.9925 & 0.298  & 0.3221 & 0.2094 & 0.4276 & 2.2108 & 1.0167 & 3.6308 &0.01217 & 0.00916\\
\hline
1.0954 & 0.2708 & 0.3615 & 0.1126 & 1.0510 & 2.7196 & 1.8428 & 4.8659 &0.01362 & 0.00721\\
\hline
\end{tabular}
\caption[Estimated Parameters on 11 different runs with high noise.]
{Estimated Parameters on 11 different runs with high noise. First row contains the true parameters,
last row contains the mean.
The red row is Run 1 and the blue row is Run 2 from  \autoref{fig:NoiseComparisonJustTwo}
and \autoref{fig:FitComparisonHighNoiseJust2}, respectively.}
\label{tab:HighNoiseResults}
\end{table}

@@

\begin{figure}[H]
\subfigure
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=\textwidth]{images/highnoise_run5_1}}
\subfigure
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=\textwidth]{images/highnoise_run5_2}}
\end{figure}

\begin{figure}[H]
\subfigure
{\label{fig:ConvergenceRuns1c} \includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=\textwidth]{images/highnoise_run5_3}}
\caption[Convergence of the parameters during run 1 of \autoref{fig:NoiseComparisonJustTwo}]
{Convergence of the parameters during run 1 of \autoref{fig:NoiseComparisonJustTwo}.
Order of estimates: $\tau_0, \alpha, E_0, V_0, \tau_s, \tau_f, \epsilon, v,
q, s, f, BOLD$.  The bars represent
a histogram, where darker bars indicate more particles with parameters in that bin. The red 
line is the parameter used to generate the true signal, blue line is the final mean of the
particles.}
\label{fig:ConvergenceRuns1}
\end{figure}

\begin{figure}[H]
\subfigure
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=\textwidth]{images/highnoise_run6_1}}
\subfigure
{\includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=\textwidth]{images/highnoise_run6_2}}
\end{figure}

\begin{figure}[H]
\subfigure
{\label{fig:ConvergenceRuns2c} \includegraphics[clip=true,trim=6cm 2cm 6cm 3cm, width=\textwidth]{images/highnoise_run6_3}}
\caption[Convergence of the parameters during run 2 of \autoref{fig:NoiseComparisonJustTwo}]
{Convergence of the parameters during run 2 of \autoref{fig:NoiseComparisonJustTwo}.
Order of estimates: $\tau_0, \alpha, E_0, V_0, \tau_s, \tau_f, \epsilon, v,
q, s, f, BOLD$.  The bars represent
a histogram, where darker bars indicate more particles with parameters in that bin. The red 
line is the parameter used to generate the true signal, blue line is the final mean of the
particles.}
\label{fig:ConvergenceRuns2}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 6cm 3.5cm,width=15cm]{images/preprocessed_noiseonly}
\caption[Preprocessed Signal for non-active, low noise signal]
{Comparison of the preprocessed signals for the low noise signal-free case.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{fig:PreprocessedNoiseOnly}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/fits_noiseonly}
\caption[Results for non-active, low noise signal]  ($\sigma_x = 0.005$, $\sigma_y = 0.01$)
{Comparison of the estimated BOLD signal for the low noise signal-free case.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$). Note the line thickness is caused
by all the estimates overlapping.}
\label{fig:fits_noiseonly}
\end{figure}

\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c |}
\hline
$\tau_0$ & $\alpha$ & $E_0$    & $V_0$    & $\tau_s$ & $\tau_f$ & $\epsilon$  & \acs{RMSR} \\
\hline
1.0324 & 0.33211 & 0.34058 & 0.03012 & 1.40665 & 2.52079 & 0.5311 &   0.00167  \\
 0.98189 & 0.33047 & 0.3386 & 0.03014 & 1.45707 & 2.47232 & 0.45049 & 0.00159   \\
 1.0429 & 0.33224 & 0.34124 & 0.02946 & 1.4618 & 2.49245 & 0.43012 &  0.00165   \\
 1.02054 & 0.3321 & 0.33484 & 0.02586 & 1.45848 & 2.48741 & 0.4193 &  0.00151   \\
 1.0565 & 0.33405 & 0.33758 & 0.02791 & 1.43784 & 2.52545 & 0.47517 & 0.00152   \\
 1.01867 & 0.33528 & 0.33918 & 0.02782 & 1.48345 & 2.49605 & 0.44209 &0.00156   \\
 1.051 & 0.33038 & 0.33837 & 0.02985 & 1.47651 & 2.48621 & 0.42719 &  0.00159   \\
 1.00281 & 0.32929 & 0.33988 & 0.0298 & 1.43519 & 2.49256 & 0.48899 & 0.00164   \\
 1.00893 & 0.33273 & 0.33982 & 0.0289 & 1.42903 & 2.49754 & 0.45688 & 0.00168   \\
 1.01289 & 0.33275 & 0.3376 & 0.02997 & 1.41188 & 2.49881 & 0.50628 & 0.00183   \\
 1.10247 & 0.33371 & 0.3419 & 0.02939 & 1.43774 & 2.53384 & 0.44079 & 0.00195   \\
\hline
1.03009 & 0.33228 & 0.33905 & 0.02902 & 1.44506 & 2.50031 & 0.46076 & 0.00165 \\
\hline
\end{tabular}
\caption{Estimated Parameters on 11 different runs with low noise and no signal present.
 ($\sigma_x = 0.005$, $\sigma_y = 0.01$)}
\label{tab:NoiseOnlyResults}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justnoise_fit_0}
\caption{Single Fit Results for non-active, low noise signal.}
\label{fig:justnoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0

\begin{figure}[H]
\centering
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/justnoise_hist_1}}
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/justnoise_hist_2}}
\end{figure}

\begin{figure}[H]
\centering
\subfigure
{\includegraphics[clip=true,trim=7cm 3cm 6cm 3cm, width=\textwidth]{images/justnoise_hist_3}}
\caption[Convergence of the parameters during a noise-only run.]
{Convergence of the parameters when the signal consisted purely of low level noise 
($\sigma_x = 0.01$, $\sigma_y = 0.005$).
Order of estimates: $\tau_0, \alpha, E_0, V_0, \tau_s, \tau_f, \epsilon, v,
q, s, f, BOLD$.  The bars represent
a histogram, where darker bars indicate more particles with parameters in that bin. The red 
line is the parameter used to generate the true signal, blue line is the final mean of the
particles. See \autoref{fig:justnoise_fit_0}}
\label{fig:JustNoiseConvergence}
\end{figure}

The data shows that the parameters did not converge
(\autoref{fig:JustNoiseConvergence}).
The peaks never even reached 1\% difference
(\autoref{fig:PreprocessedNoiseOnly}) so  the signal  stayed
well within the range of $0.005$, the standard deviation of the weighting function.
Note that the \acp{RMSR}
were actually lower than the \acp{RMSR} in the low noise simulation 
from \autoref{sec:SimLowNoise}
and the parameter estimates were more consistent across 11 runs.
The low \ac{RMSR} was caused by the overall
signal being significantly smaller than any previous simulation.
This run would benefit greatly from an adaptive weight function, since
such a much tighter weighting function would have forced the particle
filter to fail.

@@

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 2cm 5cm 3cm,width=15cm]{images/fits_noiseonly_high}
\caption[Results for non-active, high noise signal.]
{\ac{BOLD} estimates for the non-active, high noise signal ($\sigma_x = 0.1$, $\sigma_y = 0.05$). 
Note the line thickness is caused by all the estimates overlapping.}
\label{fig:fits_noiseonly_high}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[clip=true,trim=6cm 3cm 6cm 3cm,height=9cm]{images/justbignoise_fit_0}
\caption{Single Fit Results for non-active, high noise signal.}
\label{fig:justbignoise_fit_0}
\end{figure} %uses allnoise/ALLNOISE-0-w0
